Hello OpenScPCA

### 2024-03-15 analyses/hello-R/notebooks/hello.Rmd
Responses to review and linting

We will go through the processed SCE objects in the project `data` library and and count the number of cells in each object, plotting the results.

@@

# set current data dir
data_dir = file.path(repo_root, "data", "current")

@@

```{r}
ggplot(cell_counts, aes(x = n_cells, fill = project_id)) +
  geom_histogram(bins = 20) +
  labs(x = "Number of cells") +
  facet_wrap(facets = vars(project_id)) +
  guides(fill = "none") + # don't show the legend
  theme_bw()

```

@@

Now let's save the plot.
```{r}
ggsave(plot_file, width = 8, height = 6)
```

>>>>

We will go through the processed SCE objects in the project `data` library and count the number of cells in each object, plotting the results.

@@

# set current data dir
data_dir <- file.path(repo_root, "data", "current")

@@

```{r}
count_plot <- ggplot(cell_counts, aes(x = n_cells, fill = project_id)) +
  geom_histogram(bins = 20) +
  labs(x = "Number of cells") +
  facet_wrap(facets = vars(project_id)) +
  guides(fill = "none") + # don't show the legend
  theme_bw()
count_plot # show the plot
```

@@

Now let's save the plot.
```{r}
ggsave(count_plot, plot_file, width = 8, height = 6)
```
